Face recgontion using Particle Swarm clustering

### 2011-08-12 FacePaper/paper.tex
after ubuntu changes

\documentclass[a4paper, twoside]{article}

\usepackage{icgst}
%\documentclass[preprint,12pt]{elsarticle}
%\journal{Jornal Name in the document\ldots\ldots\ldots.}
\begin{document}

@@

@@

T
The remaining of the paper is organized as follows. Firstly, section
\ref{sec:section2} gives the basic background infromation on  Eigenfaces,
Particle swarm optimization,and Nelder Meed modification Section
\ref{sec:proposed} describes in details our proposed system. Section \ref{sec:Results} presents the experiments undertaken to develop the system and also some experiments to evaluate the recognition performance of the proposed system. Finally, in section \ref{sec:Conclusion} we present conclusion and future works.

@@

Now each face in the training set (minus the mean),$\Phi_i$  can be represented as a linear combination of these Eigenvectors   $u_j$:
  \begin{equation}
\Phi_i  = \sum\nolimits_{j = 1}^k {\omega_j u_j}
  \end{equation}
, where  $u_j$‘s are Eigenfaces and $\omega_j$ are the weights and can be calculated as :
\begin{equation}
\label{weighteq}
\omega _j  = u_j^T \Phi _i
\end{equation}
Each normalized training image is represented in this basis as a vector $\Omega$.
\end{enumerate}

@@

 \subsection{Nelder-Mead Enhancment}
The Nelder-Mead simplex algorithm is a derivative-free local search technique
that is capable of moving a cluster of solutions in the gradient direction and which, as per current research, can be very effectively combined with GA and PSO approaches. These hybrid evolutionary algorithms have been shown to be very successful in continuous optimization problems.
The Nelder-Mead smplex method makes use of a construct called a simplex (see
Figure 1.). When the search space is n-dimensional, the simplex consists of n+1 solutions, s,, i = {1, 2, …, n+1}, that are usually closely spaced. As shown in the top left of Figure 1., in a two-dimensional search plane, a simplex is a triangle. The fitness of each solution is considered in each step of the Nelder-Mead method, and the worst solution w is identified. The centroid, c, of the remaining n points is computed and the reflection of walong it determined. This reflection yields a new solution r that replaces w, in the next step, as shown in the top right of Figure 1. If the solution r produced by this reflection has a higher fitness than any other solution in the simplex, the simplex is further expanded along the direction of r, as shown in the middle left of the figure. On the other hand, if r has a low fitness compared to the others, the simplex is contracted. Contraction can be either outward or inward depending upon whether r is better or worse than w. The contraction operations are shown in the middle right and bottom left of the figure. If neither contraction improves the worst solution in the simplex, the best point in the simplex is computed, and a collapse is then carried out, and all the points of the simplex are moved a little closer towards the best one, as shown in the bottom right of the same figure.
\section{Proposed System}
\label{sec:proposed}

@@

The clustering algorithm prposed can be as follows:
% \begin{algorithm}
%  \caption{ Discrete Particle Swarm Algorithm }
%  \label{DPSOalg}
\begin{algorithmic}
%\begin{verbatim}

\STATE  Generate $N$ particles with $N_c$ clusters  ($P_i,$ $\dots,$ $P_{N_c}$)
\STATE Initialize the clusters centroids for each particle randomly
\FOR{i=0 \TO $t_{max}$}
  \FOR{ each particle  $p_i$}
    \FOR{ each data vector  $zp$}
        \STATE   Calculate distance $d(zp,m_{ij})$ from cluster centroid.
        \STATE   Assign $zp$ to cluster $C_{ij}$ such that
        \STATE   $d(zp,m_{ij})=min \forall k=1,\dots,N_c {d(zp,m_{ik})}$
    \ENDFOR
    \STATE  Compute the Fitness function for the particle.
     \STATE  Update the global best and local best
     \STATE  Move all particle using PSO equations.
     \ENDFOR
  \ENDFOR
 \RETURN global best
%\end{verbatim}

@@

 Figure shows the \ref{fig:pso1}

@@

\section{Conclusion}
\label{sec:Conclusion}
\section{future work}
% \subsection{Subtitle}
%
% Plain text.
%
% \subsection{Another subtitle}
%
% More plain text.
\bibliographystyle{model1a-num-names}
\bibliography{mybibfile,library}

>>>>

\documentclass[a4paper,twoside]{article}

\usepackage{icgst}
\usepackage{algorithm}
\usepackage{algorithmic}

%\documentclass[preprint,12pt]{elsarticle}
%\journal{Jornal Name in the document\ldots\ldots\ldots.}
\begin{document}

@@

The clustring algorithm is widely used to  cluster information in data and text mining and many other application \cite{}. The use of clustring algorithm in classificatin was also reproted in \cite{} where kmeans algorithms is used to lablel on the input samples to one of the trained clusters. 
The use of Particle swarm optimization (PSO) in data clustring was introduced by Merwe and Engelbrechet \cite{psoclustering}. They presented a system that was test on three different dataset and achieved better clustring than other clustring algorithms. Several enhancment has been added to the PSO algorithms to improve its efficiency and quality of the global solution. Several other search method like Nelder-Meed \cite{}  were also  integrated to the PSO algorithm. The use of Nelder-Meed search in the PSO proofed to enchance the quality of the global optimium solution with little computational cost \cite{}.

In this paper we introduce a novel face recognition algorithm that uses a Particle swarm optimization (PSO) to create clusters of faces in the database. The Nelder Meed enchancment is integarted into the PSO algorithm to create clusters where Each cluster represents a single person in the database.  The first step of the system is preprocessing the database to detect and normalize the face inside the image. Secondly, feature vectors are extracted by computing the  eigenfaces for every person in the database then extracting the wieght vector for each sample in the database. After that the training set is used to create clusters for the PSO clustering algorithm. The global solution should represents a defined center for all clusters where each cluster represent a single person. The problem of recognition of test sample is converted into identifying the cluster that the input sample belogs to. % step  %and the eigen vector are extracted. The  and

@@

The remaining of the paper is organized as follows. Firstly, section
\ref{sec:section2} gives the basic background infromation on  Eigenfaces,
Particle swarm optimization,and Nelder Meed modification Section
\ref{sec:proposed} describes in details our proposed system. Section \ref{sec:Results} presents the experiments undertaken to develop the system and also some experiments to evaluate the recognition performance of the proposed system. Finally, in section \ref{sec:Conclusion} we present conclusion and future works.

@@

Now each face in the training set (minus the mean),$\Phi_i$  can be represented as a linear combination of these Eigenvectors   $u_j$:
  \begin{equation}
\Phi_i  = \sum\nolimits_{j = 1}^k {\omega_j u_j}
  \end{equation}
, where  $u_j$?s are Eigenfaces and $\omega_j$ are the weights and can be calculated as :
\begin{equation}
\label{weighteq}
\omega _j  = u_j^T \Phi _i
\end{equation}
Each normalized training image is represented in this basis as a vector $\Omega$.
\end{enumerate}

@@

 \subsection{Nelder-Mead Enhancment}

Nelder and Meed introduced the Nelder-Mead simplex algorithm which is a deriavative free  search algorithm that finds the local minimum of function $f$ of several variables. For, more than two variable the simplex is triangle and search compares the function values at the three vertex of the tirangle. The worst solution, the largest function $f$ value, is rejected and replaced with a new vertex. The search continues as new triangle is formed and the process generates squences of triangles. %A new triangle  is formed and a new iteration of

A simplex method for finding a local minimum of a function of several variables has
been devised by Nelder and Mead. For two variables, a simplex is a triangle, and
the method is a pattern search that compares function values at the three vertices of a
triangle. The worst vertex, where f (x, y) is largest, is rejected and replaced with a new
vertex. A new triangle is formed and the search is continued. The process generates
a sequence of triangles (which might have different shapes), for which the function
values at the vertices get smaller and smaller. The size of the triangles is reduced and
the coordinates of the minimum point are found. that %

The Nelder-Mead simplex algorithm is a derivative-free local search technique
that is capable of moving a cluster of solutions in the gradient direction and which, as per current research, can be very effectively combined with GA and PSO approaches. These hybrid evolutionary algorithms have been shown to be very successful in continuous optimization problems.
The Nelder-Mead smplex method makes use of a construct called a simplex (see
Figure 1.). When the search space is n-dimensional, the simplex consists of n+1 solutions, s,, i = {1, 2,\dots  , n+1}, that are usually closely spaced. As shown in the top left of Figure 1., in a two-dimensional search plane, a simplex is a triangle. The fitness of each solution is considered in each step of the Nelder-Mead method, and the worst solution w is identified. The centroid, c, of the remaining n points is computed and the reflection of walong it determined. This reflection yields a new solution r that replaces w, in the next step, as shown in the top right of Figure 1. If the solution r produced by this reflection has a higher fitness than any other solution in the simplex, the simplex is further expanded along the direction of r, as shown in the middle left of the figure. On the other hand, if r has a low fitness compared to the others, the simplex is contracted. Contraction can be either outward or inward depending upon whether r is better or worse than w. The contraction operations are shown in the middle right and bottom left of the figure. If neither contraction improves the worst solution in the simplex, the best point in the simplex is computed, and a collapse is then carried out, and all the points of the simplex are moved a little closer towards the best one, as shown in the bottom right of the same figure.
\section{Proposed System}
\label{sec:proposed}

@@

The clustering algorithm prposed can be as follows:
% \begin{algorithm}
%  \caption{ Discrete Particle Swarm Algorithm }
%  \label{DPSOalg}
\begin{algorithmic}
%\begin{verbatim}
\STATE  Generate $N$ particles with $N_c$ clusters  ($P_i,$ $\dots,$ $P_{N_c}$)
\STATE Initialize the clusters centroids for each particle randomly
\FOR{i=0 \TO $t_{max}$}
  \FOR{ each particle  $p_i$}
    \FOR{ each data vector  $zp$}
        \STATE   Calculate distance $d(zp,m_{ij})$ from cluster centroid.
        \STATE   Assign $zp$ to cluster $C_{ij}$ such that
        \STATE   $d(zp,m_{ij})=min \forall k=1,\dots,N_c {d(zp,m_{ik})}$
    \ENDFOR
    \STATE  Compute the Fitness function for the particle.
     \STATE  Update the global best and local best
     \STATE  Move all particle using PSO equations.
     \ENDFOR
  \ENDFOR
 \RETURN global best
%\end{verbatim}

@@

 Figure shows the \ref{fig:pso1} the block diagram for the PSO clustering algorithm.

@@

\section{Conclusion}
\label{sec:Conclusion}
\section{future work}
% \subsection{Subtitle}
%
% Plain text.
%
% % \subsection{Another subtitle}
%
% More plain text.
\bibliographystyle{model1a-num-names}
\bibliography{mybibfile,library}
